Combinatorics of the geometry of Wilson loop diagrams II: Grassmann necklaces, dimensions, and denominators

### 2019-06-17 GWLDCII.tex
very minor edits (as discussed) to 1, incorporated Susama's changes to 2 as far as the end of section 4

\begin{rmk}
The following observation will be very useful in many of the arguments below.

Suppose we are going through the algorithm to construct $I_i^W$ and we are currenctly at step $j$ of the loop.  Consider the diagram $W'$ formed by $W$ with all the propagators already contributed removed; think of a vertex being taken away when it is contributed, since it can only contribute once, so it is gone from the point of view of the rest of the construction of $I_i^W$.  Now suppose for some other diagram $V$ on the same vertex set we are constructing $I_k^V$ and we are at step $j$ of the loop, for the same $j$ as above.  Again let $V'$ be $V$ with all the propagators already contributed removed.

With this setup, if there is an interval, $(j-1, \ldots, \ell+1)$ (with $\ell <_i i$ and $\ell <_k k$) in $W'$ and $V'$ where the propagators ending in that interval are identical in both diagrams, then the construction of $I_i^W$ and $I_k^V$ is identical up to and including step $\ell$.  The constructions are identical for those steps simply because the local situation of propagators supported at $j, j+1, \ldots, \ell$ is identical in both cases and the algorithm only sees the local situation at the vertex corresponding to the current step.
\end{rmk}

@@

Let $W = (\cP,[n])$ be an admissible Wilson loop diagram, and $p = (i,j) \in \cP$.  Then $J_p^{W}(i)$, $J_p^{W}(i+1)$, $J_p^{W}(j)$, and $J_p^{W}(j+1)$ are each non-empty cyclic intervals which partition $[n]$ and occur in the given cyclic order.
\end{lem}

@@

We first calculate $I^{W}_w$ for a starting vertex ${w \in [n]\backslash \{l, l+1, \ldots,j,j+1\}}$. Note that $p$ has no effect on other propagators for starting vertices in this range, so if $r \neq p$, then $I_w^W(r) = I_w^V(r)$. Meanwhile, the value of $I^{W}_w(p)$ depends on which step in the algorithm the propagator $q$ is assigned to a vertex, i.e. on the value of $I^{V}_w(q)$. Thus, if $w\in J_q^{V}(i)$ then 
    \[
    I_w^{W}(r) =  \begin{cases}
        \max\{i+1, m\} & \text{if } r=p \\
        I_{w}^{V}(r) & \text{if } r\neq p
      \end{cases} 
    \]
    while if $w\in J_q^{V}(i+1)$ or $w\in J_q^{V}(j)$ then
    \[
    I_w^{W}(r) =  \begin{cases}
        l & \text{if } r=p \\
        I_{w}^{V}(r) & \text{if } r\neq p
      \end{cases} 
      \]
We also need to understand $I^{W}_w$ for $w \in \{l,l+1,\ldots,j,j+1\}$. For the majority 
%$w \in [l, l+a-1]$} 
%I left this as a comment so we can add it in if necessary, but I don't think we need this level of precision in this sentence: we're just signposting what we're going to do in detail shortly.
of these vertices, we use the following observation: if $p$ is the first propagator to be assigned a value by $I_w^{W}$, then the remainder of $I_w^{W}$ proceeds identically to the assignments of $I^{V}_{w+1}$.  Thus we have for any $0\leq b <a$
    \[
    I_{l+b}^{W}(r) = \begin{cases}
      l+b & \text{if } r=p\\
      I_{l+b+1}^{V}(r) & \text{if } r\neq p
    \end{cases}
    \]
Similarly, if $j$ is in the support of $p$, then we have
     \[
       I_j^{W}(r) = \begin{cases}
         j & \text{if $r=p$ and $j$ is in the support of $p$}\\
         I_{j+1}^{V}(r) & \text{if $r\neq p$ and $j$ is in the support of $p$}\\
       \end{cases}
       \]
If $j$ is not in the support of $p$, then we must be in the second case of Figure~\ref{fig 3 cases} with two vertices in the right hand region.  In this case, if we start the algorithm at $j$ we need to know whether there will be any unassigned propagators other than $p$ when we reach vertex $i$, so as to know what $p$ contributes.

@@

\note{Sian is here}

\begin{thm}\label{res:alg gives GN}
The sequence of $k$-subsets $(I_1,\dots,I_n)$ obtained by applying Algorithm~\ref{alg:put GN on WLD} to all vertices of an admissible diagram $W$ is exactly the Grassmann necklace of $M(W)$.
\end{thm}
\note{Sian replaced all occurences of $k$ as an index with other letters: someone please proofread this specifically to check that none were missed! (then remove this note)}
\begin{proof}
For each $i \in [n]$, let $I_i$ be the set of vertices assigned to the propagators of $W$ by Algorithm~\ref{alg:put GN on WLD} with starting vertex $i$. By Lemma~\ref{GN alg well defined}, we know that $|I_i| = k$ for each $i \in [n]$. We first prove that $I_{i+1} \supseteq I_i \backslash \{i\}$ for all $i \in [n]$; this is equivalent to the definition of Grassmann necklace given in Definition~\ref{def:grassmann necklace}.

@@

\textbf{Case I}:  Suppose $p$ has one end on edge $i-1$.  \st{Then} {\color{violet}If} $p$ is not supported on $i+1$, \st{so} in building $I_{i+1}$ \hlfix{we will assign the same propagators as in the construction of $I_i$from vertices $i+1$ up to $b-1$, that is $I_{i+1} \cap [i+1,b-1] = I_{i} \cap [i+1,b-1]$}{Lemma-ize?}.  {\color{violet} (If $p$ is supported on $i+1$, $b= i+1$ and the interval $[i+1,b-1]$ is emptry.)} Furthermore, by Lemma~\ref{vertex cyclic int lem}, when building $I_{i+1}$ it must happen that $p$ contributes vertex $b$, as otherwise $b$ would never be contributed by $p$. Consequently, in building $I_{i+1}$, when the algorithm reaches vertex $b$ there cannot be any unassigned propagators remaining that are \hlfix{before}{do we have an ordering on $\cP$?} $p$.  This is also true in when the algorithm constructing $I_i$ reaches $b$, since the \hlfix{same propagators have been assigned beforehand}{see above.}.  Finally, we also note that $m\geq_i b+1$.

@@

By the above observations, if we commence Algorithm~\ref{alg:put GN on WLD} in $W'$ from vertex $b$, then we are in the same situation with respect to unassigned propagators as if we began at $i$ in $W$ and proceeded to $b$ following the algorithm {\color{violet}(recall that $I^W_i(p) =i$)}\st{; the propagators we assigned in the latter case}{\color{violet}. The propagators contributing to $I_{i}$ for $W$ before the vertex $b$} are exactly the ones removed to build $W'$.  Similarly, starting at $i+1$ in $W$ and moving to $b+1$ leaves us in the same situation with respect to unassigned propagators as beginning at $b+1$ in $W'$ would.  This gives the equations
\begin{align*}
  I_i^{W} \cap [b,i-1] & = I_b^{W'} \\
  I_{i+1}^{W} \cap [b+1,i-1] & = I_{b+1}^{W'}
\end{align*} \sanote{ $I_i^{W}$ is a map not a $k$-tuple. Do we mean $I_i$ for $W$? or $I_i^{W}(\cP)$ because we want the image set?}
where the diagram is indicated in the superscript.
Thus we have $m\in I_b^{W'}\setminus\{b\}$ and $m\not\in I_{b+1}^{W'}$, contradicting the minimality of $(W, i, m)$.

\textbf{Case II}: Suppose $p$ has one end on edge $i$.  Note that by assumption we have $I_i(p) = i$; this means that $p$ must be the \st{first} {\color{violet} counterclockwise most} propagator lying on edge $i$, and hence we must have $I_{i+1}(p) = i+1$ as well.  Observe also that $m\geq_i i+2$ since $i+1\in I_{i+1}$.

@@

%If $i \not\in I_i$, then there are no propagators supported on $i$ at all.  In this case it is clear that applying Algorithm~\ref{alg:put GN on WLD} at vertex $i$ and vertex $i+1$ produces exactly the same result, i.e. $I_{i+1} = I_i$.
%
%Now suppose that $i \in I_i$.  Order $I_i$ and $I_{i+1}$ with respect to $\leq_{i+1}$; in particular, $i$ is the last term in $I_i$ with respect to this ordering.
%
%Let $p_1$ be the rightmost propagator supported on $i$, and suppose it is removed at step $a$ with respect to vertex $i+1$.  This is the first point at which $I_{i+1}$ can differ from $I_i$, i.e. we have $I_{i+1} \cap \interval{i+1}{a-1} = I_{i} \cap \interval{i+1}{a-1}$.  If $a \not\in I_i$, then $p_1$ is the only propagator supported on $a$ at step $a$ with respect to vertex $i+1$.  All remaining steps are unchanged and we conclude that $I_{i+1} = I_i \backslash \{i\} \cup \{a\}$.
%
%If $a \in I_i$, then at step $a$ with respect to vertex $i+1$ there must be another propagator $p_2$ which lies to the left of $p_1$.  We have $I_{i+1} \cap \interval{i+1}{a} = I_i \cap \interval{i+1}{a}$, and the next possible difference
%
%{\color{red}[argh]}
%
%Although there are many different subcases to consider, the idea is always the same: we look for the first entry where $I_{i+1}$ and $I_i \backslash \{i\}$ differ (with respect to $<_{i+1}$), and show that this is the only possible difference.
%
%The reader should keep in mind that due to Proposition~\ref{res:alg k labels}, the following process cannot double back on itself.
%
%\begin{enumerate}
%\item If $p_1$ contributes $k$ to $I_{i+1}$ and $k \in I_i$, then there is another propagator $p_2$ which was deleted at step $k$ with respect to vertex $i$, but now survives at step $k$ with respect to vertex $i+1$.  All intermediate steps of the algorithm are unchanged, so $I_{i+1}$ and $I_i \backslash \{i\}$ agree up to (and including) $k$.
%\item We now look at which label $p_2$ contributes in $I_{i+1}$, and apply the same argument.  Iterate this process until we find a propagator $p_r$ which is deleted at step $j$ with respect to vertex $i+1$, but $j \not\in I_i$.
%\item $j \not\in I_i$ implies that $p_r$ is the \textit{only} propagator supported on vertex $j$ at this step.  There is therefore no knock-on effect, and any remaining propagators in the diagram contribute the same label to both $I_i$ and $I_{i+1}$. We conclude that $I_{i+1} = I_i \backslash \{i\} \cup \{j\}$.
%\end{enumerate}

@@

We have shown that $(I_1,\dots,I_n)$ is a Grassmann necklace; it remains to check that this Grassmann necklace corresponds to the positroid $M(W)$.  {\color{violet} By equation \eqref{basesofmatroids}, w}e need to show that: \sanote{added a number to this eq. make it a dfn?}
\begin{itemize}
\item For each $i \in [n]$, $I_i$ is a basis for $M(W)$.
\item If $J$ is lexicographically smaller than {\color{violet} any} $I_i$ with respect to $<_i$, then $J$ is not a basis for $M(W)$. 
\end{itemize}
The first point follows immediately: since the algorithm is pairing each $j \in I_i$ with a unique propagator supported on that vertex, $I_i$ is a basis for $M(W)$ by Corollary~\ref{lem basis as perm}.

@@

\begin{proof}
  By Algorithm~\ref{alg:put GN on WLD} the Grassmann necklace of $W$ is obtained from the Grassmann necklace of $V$ by duplicating the $i$th element of the Grassmann necklace of $V$ (shifting indices by $1$ for all indices greater than $i$) \sanote{changed a bit of wording on the proof}, and incrementing all indices greater than $i$ by $1$ in each Grassmann necklace element.  Formally, if $I_1^{V}, \ldots, I_{n-1}^{V}$ and $I_1^{W}, \ldots, I_n^{W}$ are the Grassmann necklaces of $V$ and $W$ respectively then
  \[
  I_j^{W} =
  \begin{cases}
    \{\ell \in I_j^{V} : \ell < i\} \cup \{\ell+1 \in I_j^{V} : \ell \geq i\} & \text{if $j\leq i$} \\
    \{\ell \in I_{j-1}^{V} : \ell < i\} \cup \{\ell+1 \in I_{j-1}^{V} : \ell \geq i\} & \text{if $j > i$.}
  \end{cases}
  \]

@@

\begin{lem}\label{lem good p}
  Let $W$ be an admissible Wilson loop diagram with $n\geq 1$ propagators.  Then there is some dihedral transformation $W'$ of $W$ such that $W'$ has a propagator $p$ with the following properties.
  \begin{itemize}
  \item $p = (i, n-1)$ for some $i$, and $p$ has no propagators inside it (that is $i+2, \ldots, n-2$ do not support any propagators in $W'$).
  \item Either the edge $i$ in $W'$ only supports $p$ or the edge $i$ in $W'$ supports exactly one other propagator \hlfix{$q = (i, j)$ with no other propagators inside $q$ in the $<_i$ ordering, and $j <_1 i$.}{changed. Correct? Explicitly, not letting $i <_i j <_i n-1$. Also made this change below. } 
  \end{itemize}
\end{lem}

@@

Combining Lemmas \ref{lem uncovered}, \ref{lem dihedral}, and \ref{lem good p}, it therefore suffices to study the Le diagrams of weakly admissible Wilson loop diagrams with $F(\emptyset)  = \emptyset$, admitting one of the configurations described in Lemma \ref{lem good p} with propagators \hlfix{$p = (n-3, n-1)$ and $q= (n-5, n-3)$}{changed. correct?} (if $q$ exists) both of length 2. See Figure~\ref{fig special p} for an illustration of the two possibilities.

@@

Next consider $I_n^{W}$. From the figure we see that in both cases we have $I_n^{W}(p) = n$. At vertex 1 of the algorithm $I_n$, the unassigned propagators are exactly those that appear in $V$.\sanote{same invisible lemma} Therefore the algorithm continues as in $I_1^{V}$, i.e. we have $I_n^{W} = I_1^{V} \cup \{n\}$. By a similar argument, we must have $I_{n-1}^{W} = I_n^{V} \cup \{n-1\}$.

@@

\note{When doing the final formatting, try to ensure that Figure \ref{fig Le} and Lemma \ref{lem shape} are on the same page}
\begin{lem}\label{lem shape}
  Let $V$ and $W$ be as in Lemma~\ref{lem I}.
  The shape of the Le diagram of $V$ can be built from left to right of the following blocks: a rectangle which is 3 columns wide, one more column of the same height, and a \hl{partition shape}\sanote{Is this defined? shape defined by $I_i$?} with at most as many rows as the rectangle.
  The shape of the Le diagram of $W$ can be built from left to right of the following blocks: a rectangle with 3 columns and one more row than the first rectangle of $V$, and the same partition shape as in $V$.
\end{lem}

@@

Recall that $I_1$ determines the shape of the Le diagram. By the arguments in Lemma~\ref{lem I} we know that ${n,n-1,n-2, n-3 \not\in I_1^{V}}$ (which yields the leftmost four columns of the diagram for $V$) and that $I_1^{W} = I_1^{V}\cup \{n-3\}$. This implies that the right hand boundary of the shape of $V$ is the same as the right hand boundary of the shape of $W$ except that $W$ has one additional row of 3 boxes while $V$ has an additional column in the $n-3$ position; that is, an extra column fourth from the left. \sanote{Can we rephrase this in terms of row and column numbers (as in section 2) rather than use shape?}
\end{proof}

@@

% Additionally $n-3\not\in I_{n}^{V}$ since if it were then $n-3$ would also be in $I_1^{V}$ and hence propagator $p$ could not contribute $n-3$ to $I_1^{W}$ in contradiction to Lemma~\ref{vertex cyclic int lem}.  Similarly $n-1, n-2\not\in I_n^{V}$.  Thus the paths putting the plusses in from $I_n^{V}$ lie completely in $\mathcal{B}$ or take some vertical boundary edge $>n-3$ to $n$.   Now view these paths in the Le diagram of $W$ and note that the path $n-3\rightarrow n-1$ is compatible, and so these paths together build the plusses that $I_{n-1}^{W}$ contributes.  That is, we get all the plusses from $I_{n}^{V}$ along with a $n-3\rightarrow n-1$ plus, that is a plus in the second to the right box of the bottom row.

@@

%\begin{lem}\label{lem n-2 bad}
%Let $V$ and $W$ be as in Lemma~\ref{lem I}, and suppose that $n-2,n-1 \in I_{n-2}^{V}$.
%
%Then $I_{n-2}^{W}$ and $I_{n-3}^{W}$ contribute the following plusses to the Le diagram of $W$
%  \begin{itemize}
%  \item An $(n-3)\rightarrow (n-2)$ plus and an $(n-5)\rightarrow (n-1)$ plus.
%  \item All of the $I_{n-1}^{V}$ plusses.
%  \item In the Le diagram of $V$, $I_{n-2}^{V}$ contributes an $n-5\rightarrow n-2$ plus and no other term in the Grassmann necklace of $V$ gives a plus in this column.  $I_{n-2}^W$ does not contribute this $+$ but yields an $n-5\rightarrow n-1$ plus instead.
%  \item All other plusses of $I_{n-2}^{V}$.
%  \item In the Le diagram of $V$, $I_{n-3}^{V}$ gives a plus in the $n-3$ column.  This $+$ is shifted over into the $n-2$ column in $W$.
%  \item All other plusses of $I_{n-3}^{V}$.
%  \end{itemize}
%Furthermore, no element of the Gramann necklace of $V$ gives an $n-5\rightarrow n-1$ plus.
%\end{lem}
%
%\begin{proof}
%  By Lemma~\ref{lem I} $I_{n-2}^{W}= (I_{n}^{V} - \{n-5\})\cup \{n-1,n-2\}$.  Also, by the location of $q$ in the WLD,  $n-2\not\in I_{n-3}^{V}$ and and $n-5$ is the index of the lowest vertical edge in $\mathcal{B}$.  Thus this section of the Gramann necklace of $V$ looks like
%  \begin{equation}\label{eq necklace}
%  I_{n-3}^{V} \underset{\substack{n-3\text{ out}\\n-2\text{ in}}}{\rightarrow} I_{n-2}^{V} \underset{\substack{n-2\text{ out}\\n-5\text{ in}}}{\rightarrow} I_{n-1}^{V} \underset{\substack{n-1\text{ out}\\\text{something in}}}{\rightarrow} I_{n}^{V} \underset{\substack{n \text{ out}\\\text{something in}}}{\rightarrow} I_1^{V}
%  \end{equation}
%  where the first ``something'' is either $n$ or an element of $I_1^{V}$ and the second ``something'' is an element of $I_1^{V}$.  Additionally all elements not explicitly mentioned must be in $I_1^{V}$ as they remain unchanged through this portion of the necklace.
%
%  Using this information now determine the symmetric difference of $I_{n-2}^{V}$ and $I_1^{V}$: $n-1, n-2$ and possibly $n$ are in $I_{n-2}^{V}$ but not in $I_1^{V}$.  $n-5$ is in $I_1^{V}$ as are at least one and at most two other elements.  If there is one such element call it $a$.  If there are two call them $a$ and $b$ with $a>b$.  This means that the plusses in the Le diagram of $V$ coming from $I_{n-2}^{V}$ are as in the first part of Figure~\ref{fig messy}.  Stepping to $I_{n-1}^{V}$ simply removes the $n-5\rightarrow n-2$ path, see the second part of Figure~\ref{fig messy}.
%
%  \begin{figure}
%    \includegraphics{messy}
%    \caption{Plusses coming from $I_{n-2}^{V}$ (top left),  $I_{n-1}^{V}$ (top right) and $I_{n}^{V}$ bottom when $n-1, n-2\in I_{n-1}^{V}$.  The blue lines are the non-intersecting paths.  The dashed blue lines may or may not appear, but if one appears then they both do.}\label{fig messy}
%  \end{figure}
%
%  Stepping to $I_{n}^{V}$, $n-1$ is taken out and either $n$ is put in if it was not there before, or one of $a$ or $b$ is put in and hence no longer available as a right end for a path.  This gives two possible configurations illustrated in the bottom two parts of Figure~\ref{fig messy}.
%
%  Now we know that $I_{n-2}^{W}  = (I_{n}^{V} - \{n-5\})\cup \{n-1,n-2\}$ so the paths for building plusses from $I_{n-2}^{W}$ go from the set $\{n-5, n-3\}$ along with whichever of $a$ and $b$ is not in $I_{n}^{V}$ to $\{n-2, n-1, n\}$.  This means that we get plusses as in Figure~\ref{fig messyD} where the left and right cases correspond to the left and right cases in the bottom parts of Figure~\ref{fig messy}
%
%  \begin{figure}
%     \includegraphics{messyD}
%    \caption{Plusses coming from $I_{n-2}^{W}$.}\label{fig messyD}
%  \end{figure}
%
%  This proves the first item of statement of the lemma.
%
%  Now consider $I_{n-3}^{V}$.  By \eqref{eq necklace} $I_{n-3}^{V}$ contributes the same plusses as $I_{n_2}^{V}$ except that it contributes an $n-5\rightarrow n-3$ plus in place of the $n-5\rightarrow n-2$ plus.  Also, we have $n-3\in I_{n-3}^{V}$ be the location of $q$ and so $I_{k}^{W} = I_k^{V}\cup\{n-2\}$.  Thus the paths for $I^{W}_{n-3}$ are the same as for $I^{V}_{n-3}$ except that the path that did go to $n-3$ now goes to $n-2$.  This cannot conflict with another path since \eqref{eq necklace} shows that $n-2$ only appears in $I_{n-2}^{V}$ among the necklace elements of $V$.
%
%  Also note that $I_{n-3}^{V}, I_{n-2}^{V}$, and $I_{n-1}^{V}$ share their plusses outside of the $n-3$ and $n-2$ columns.  This proves the remaining statements of the lemma except the furthermore.
%
%  Finally, suppose there were a $n-5\rightarrow n-1$ plus in the Le diagram of $V$.  By the algorithm, it would have to come when $n-5 \not\in I_j^{V}$.  By \eqref{eq necklace} this means that it would have to come from $I_{n-4}^{V}$, $I_{n-3}^{V}$, or $I_{n-2}^{V}$. The analysis above shows it does not come from $I_{n-3}^{V}$ or $I_{n-2}^{V}$.   Now, $n-4\in I_{n-4}^{V}$ by the location of $q$ and so $I_{n-4}^{V}$ must give an $n-5\rightarrow n-4$ plus and so cannot give an $n-5\rightarrow n-1$ plus.
%
%\end{proof}

@@

\begin{proof}
  By Lemma~\ref{lem I} we have $I_{n-2}^{W}= (I_{n}^{V} \setminus \{n-5\})\cup \{n-1,n-2\}$ and $I_1^W = I_1^V\cup \{n-3\}$. We are necessarily in the case where $W$ admits a propagator $q$ (the right hand case of Figure~\ref{fig special p}) and we can see from the location of $q$ that $n-2\not\in I_{n-3}^{V}$ and that $n-5$ \hlfix{is the label of the last row in}{would like to propagate changes like this through.} $\mathcal{B}$.  Also note that by Lemma~\ref{vertex cyclic int lem} and Corollary~\ref{no coloops} we must have $n\in I_n^V$. Thus this section of the Grassmann necklace of $V$ looks like

>>>>

\begin{rmk}\label{rmk algorithm locally same}
The following observation will be very useful in many of the arguments below.

Suppose we are going through the algorithm to construct $I_i^W$ for some $i$, and we are currently at step $j$ of the loop.  Consider the diagram $W'$ formed by $W$ with all the propagators already contributed removed; think of a vertex being taken away when it is contributed, since it can only contribute once, so it is gone from the point of view of the rest of the construction of $I_i^W$.  Now suppose for some other diagram $V$ on the same vertex set we are constructing $I_m^V$ for some $m$, and we are at step $j$ of the loop, for the same $j$ as above.  Again let $V'$ be $V$ with all the propagators already contributed removed.

With this setup, if there is an interval, $(j-1, \ldots, \ell+1)$ (with $\ell <_i i$ and $\ell <_m m$) in $W'$ and $V'$ where the propagators ending in that interval are identical in both diagrams, then the construction of $I_i^W$ and $I_m^V$ is identical up to and including step $\ell$.  The constructions are identical for those steps simply because the local situation of propagators supported at $j, j+1, \ldots, \ell$ is identical in both cases and the algorithm only sees the local situation at the vertex corresponding to the current step.
\end{rmk}

@@

Let $W = (\cP,[n])$ be an admissible Wilson loop diagram, and $p = (i,j) \in \cP$.  Then $J_p^{W}(i)$, $J_p^{W}(i+1)$, $J_p^{W}(j)$, and $J_p^{W}(j+1)$ are each non-empty cyclic intervals which partition $[n]$ and occur in the given cyclic order.
\end{lem}
\note{Right at the end when we put the tikz figures in, someone needs to go through this proof and replace ``leftmost two cases'' with ``Case 1 and 2'' etc, because the tikz picture is arranged differently}

@@

We first calculate $I^{W}_w$ for a starting vertex ${w \in [n]\backslash \{l, l+1, \ldots,j,j+1\}}$. Note that $p$ has no effect on other propagators for starting vertices in this range, so if $r \neq p$, then $I_w^W(r) = I_w^V(r)$. Meanwhile, the value of $I^{W}_w(p)$ depends on which step in the algorithm the propagator $q$ is assigned to a vertex, i.e. on the value of $I^{V}_w(q)$. Thus, if $w\in J_q^{V}(i)$ then 
    \[
    I_w^{W}(r) =  \begin{cases}
        \max\{i+1, m\} & \text{if } r=p \\
        I_{w}^{V}(r) & \text{if } r\neq p
      \end{cases} 
    \]
    while if $w\in J_q^{V}(i+1)$ or $w\in J_q^{V}(j)$ then
    \[
    I_w^{W}(r) =  \begin{cases}
        l & \text{if } r=p \\
        I_{w}^{V}(r) & \text{if } r\neq p
      \end{cases} 
      \]
We also need to understand $I^{W}_w$ for $w \in \{l,l+1,\ldots,j,j+1\}$. For the majority 
%$w \in [l, l+a-1]$} 
%I left this as a comment so we can add it in if necessary, but I don't think we need this level of precision in this sentence: we're just signposting what we're going to do in detail shortly.
of these vertices, we use the following observation: if $p$ is the first propagator to be assigned a value by $I_w^{W}$, then the remainder of $I_w^{W}$ proceeds identically to the assignments of $I^{V}_{w+1}$ (recall Remark~\ref{rmk algorithm locally same}).  Thus we have for any $0\leq b <a$
    \[
    I_{l+b}^{W}(r) = \begin{cases}
      l+b & \text{if } r=p\\
      I_{l+b+1}^{V}(r) & \text{if } r\neq p
    \end{cases}
    \]
Similarly, if $j$ is in the support of $p$, then we have
     \[
       I_j^{W}(r) = \begin{cases}
         j & \text{if $r=p$ and $j$ is in the support of $p$}\\
         I_{j+1}^{V}(r) & \text{if $r\neq p$ and $j$ is in the support of $p$}\\
       \end{cases}
       \]
If $j$ is not in the support of $p$, then we must be in the second case of Figure~\ref{fig 3 cases} with two vertices in the right hand region.  In this case, if we start the algorithm at $j$ we need to know whether there will be any unassigned propagators other than $p$ when we reach vertex $i$, so as to know what $p$ contributes.

@@

\begin{thm}\label{res:alg gives GN}
The sequence of $k$-subsets $(I_1,\dots,I_n)$ obtained by applying Algorithm~\ref{alg:put GN on WLD} to all vertices of an admissible diagram $W$ is exactly the Grassmann necklace of $M(W)$.
\end{thm}
\begin{proof}
For each $i \in [n]$, let $I_i$ be the set of vertices assigned to the propagators of $W$ by Algorithm~\ref{alg:put GN on WLD} with starting vertex $i$. By Lemma~\ref{GN alg well defined}, we know that $|I_i| = k$ for each $i \in [n]$. We first prove that $I_{i+1} \supseteq I_i \backslash \{i\}$ for all $i \in [n]$; this is equivalent to the definition of Grassmann necklace given in Definition~\ref{def:grassmann necklace}.

@@

\textbf{Case I}:  Suppose $p$ has one end on edge $i-1$.  If $p$ is not supported on $i+1$, then in building $I_{i+1}$ we will assign the same propagators as in the construction of $I_i$ from vertices $i+1$ up to $b-1$, that is $I_{i+1} \cap [i+1,b-1] = I_{i} \cap [i+1,b-1]$.  (If $p$ is supported on $i+1$, then $b= i+1$ and the interval $[i+1,b-1]$ is empty.) Furthermore, by Lemma~\ref{vertex cyclic int lem} it must happen that $p$ contributes vertex $b$ to $I_{i+1}$, as otherwise $b$ would never be contributed by $p$. Consequently, in building $I_{i+1}$, when the algorithm reaches vertex $b$ there cannot be any remaining unassigned propagators that are supported on $b$ and counterclockwise of $p$.  This is also true in when the algorithm constructing $I_i$ reaches $b$, since the same propagators have been assigned beforehand.  Finally, we also note that $m\geq_i b+1$.

@@

By the above observations, if we commence Algorithm~\ref{alg:put GN on WLD} in $W'$ from vertex $b$, then we are in the same situation with respect to unassigned propagators as if we began at $i$ in $W$ and proceeded to $b$ following the algorithm (recall that $I^W_i(p) =i$). The propagators contributing to $I_{i}^W$ before the vertex $b$ are exactly the ones removed in the construction of $W'$.  Similarly, starting at $i+1$ in $W$ and moving to $b+1$ leaves us in the same situation with respect to unassigned propagators as beginning at $b+1$ in $W'$ would.  This gives the equations
\begin{align*}
  I_i^{W} \cap [b,i-1] & = I_b^{W'} \\
  I_{i+1}^{W} \cap [b+1,i-1] & = I_{b+1}^{W'}
\end{align*} 
where the diagram is indicated in the superscript.
Thus we have $m\in I_b^{W'}\setminus\{b\}$ and $m\not\in I_{b+1}^{W'}$, contradicting the minimality of $(W, i, m)$.

\textbf{Case II}: Suppose $p$ has one end on edge $i$.  Note that by assumption we have $I_i(p) = i$; this means that $p$ must be the counterclockwise-most propagator lying on edge $i$, and hence we must have $I_{i+1}(p) = i+1$ as well.  Observe also that $m\geq_i i+2$ since $i+1\in I_{i+1}$.

@@

@@

We have shown that $(I_1,\dots,I_n)$ is a Grassmann necklace; it remains to check that this Grassmann necklace corresponds to the positroid $M(W)$.  Recall from the discussion following Definition~\ref{def:grassmann necklace}, and equation \eqref{basesofmatroids} in particular, that it suffices to show: 
\begin{itemize}
\item For each $i \in [n]$, $I_i$ is a basis for $M(W)$.
\item If $J$ is lexicographically smaller than $I_i$ with respect to $<_i$ (for any $i \in [n]$) then $J$ is not a basis for $M(W)$. 
\end{itemize}
The first point follows immediately: since the algorithm is pairing each $j \in I_i$ with a unique propagator supported on that vertex, $I_i$ is a basis for $M(W)$ by Corollary~\ref{lem basis as perm}.

@@

\begin{proof}
  By Algorithm~\ref{alg:put GN on WLD} the Grassmann necklace of $W$ is obtained from the Grassmann necklace of $V$ by duplicating the $i$th element of the Grassmann necklace of $V$ (shifting indices by $1$ for all indices greater than $i$), and incrementing all indices greater than $i$ by $1$ in each Grassmann necklace element.  Formally, if $I_1^{V}, \ldots, I_{n-1}^{V}$ and $I_1^{W}, \ldots, I_n^{W}$ are the Grassmann necklaces of $V$ and $W$ respectively then
  \[
  I_j^{W} =
  \begin{cases}
    \{\ell \in I_j^{V} : \ell < i\} \cup \{\ell+1 \in I_j^{V} : \ell \geq i\} & \text{if $j\leq i$} \\
    \{\ell \in I_{j-1}^{V} : \ell < i\} \cup \{\ell+1 \in I_{j-1}^{V} : \ell \geq i\} & \text{if $j > i$.}
  \end{cases}
  \]

@@

\begin{lem}\label{lem good p}
  Let $W$ be an admissible Wilson loop diagram with $n\geq 1$ propagators.  Then there is some dihedral transformation $W'$ of $W$ such that $W'$ has a propagator $p$ with the following properties.
  \begin{itemize}
  \item $p = (i, n-1)$ for some $i$, and $p$ has no propagators inside it w.r.t the $<_i$ ordering (that is $i+2, \ldots, n-2$ do not support any propagators in $W'$).
  \item Either the edge $i$ in $W'$ only supports $p$, or the edge $i$ in $W'$ supports exactly one other propagator $q = (j,i)$, with no other propagators inside $q$ in the $<_j$ ordering. \note{Sian undid Susama's change here: all we know about $q$ is that it goes from some edge $j$ to $i$, and there's nothing inside $q$ wrt that orientation. In a very degenerate case, $q$ could probably be $(n,i)$.}
  \end{itemize}
\end{lem}

@@

Combining Lemmas \ref{lem uncovered}, \ref{lem dihedral}, and \ref{lem good p}, it therefore suffices to study the Le diagrams of weakly admissible Wilson loop diagrams with $F(\emptyset)  = \emptyset$, admitting one of the configurations described in Lemma \ref{lem good p} with propagators $p = (n-3, n-1)$ and $q= (n-5, n-3)$ (if $q$ exists) both of length 2. See Figure~\ref{fig special p} for an illustration of the two possibilities.

@@

Next consider $I_n^{W}$. From the figure we see that in both cases we have $I_n^{W}(p) = n$. At vertex 1 of the algorithm $I_n$, the unassigned propagators are exactly those that appear in $V$. Therefore the algorithm continues as in $I_1^{V}$ (recall Remark~\ref{rmk algorithm locally same} about locally identical propagator configurations), i.e. we have $I_n^{W} = I_1^{V} \cup \{n\}$. By a similar argument, we must have $I_{n-1}^{W} = I_n^{V} \cup \{n-1\}$.

@@

\note{When doing the final formatting, try to ensure that Figure \ref{fig Le} and Lemma \ref{lem shape} are on the same page}
\begin{lem}\label{lem shape}
  Let $V$ and $W$ be as in Lemma~\ref{lem I}.
  The shape of the Le diagram of $V$ can be built from left to right of the following blocks: a rectangle which is 3 columns wide, one more column of the same height, and a partition shape with at most as many rows as the rectangle.
  The shape of the Le diagram of $W$ can be built from left to right of the following blocks: a rectangle with 3 columns and one more row than the first rectangle of $V$, and the same partition shape as in $V$.
\end{lem}

@@

Recall that $I_1$ determines the shape of the Le diagram: specifically, the elements of $I_1$ label the rows of the diagram, working from top right to bottom left. By the arguments in Lemma~\ref{lem I} we know that ${n,n-1,n-2, n-3 \not\in I_1^{V}}$ (which yields the leftmost four columns of the diagram for $V$) and that $I_1^{W} = I_1^{V}\cup \{n-3\}$. This implies that the right hand boundary of the shape of $V$ is the same as the right hand boundary of the shape of $W$ except that $W$ has one additional row of 3 boxes while $V$ has an additional column in the $n-3$ position; that is, an extra column fourth from the left. 
\sanote{Can we rephrase this in terms of row and column numbers (as in section 2) rather than use shape?}
\end{proof}

@@

@@

@@

\begin{proof}
  By Lemma~\ref{lem I} we have $I_{n-2}^{W}= (I_{n}^{V} \setminus \{n-5\})\cup \{n-1,n-2\}$ and $I_1^W = I_1^V\cup \{n-3\}$. We are necessarily in the case where $W$ admits a propagator $q$ (the right hand case of Figure~\ref{fig special p}) and we can see from the location of $q$ that $n-2\not\in I_{n-3}^{V}$ and that $n-5$ is the label of the last row in $\mathcal{B}$.  Also note that by Lemma~\ref{vertex cyclic int lem} and Corollary~\ref{no coloops} we must have $n\in I_n^V$. Thus this section of the Grassmann necklace of $V$ looks like
